Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
typo

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}

@@

In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connecting structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}

@@

In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
